Distributions

### 2021-12-27 Ch2_distributions/Ch2_Figures.Rmd
Figure 2 titles and captions

# Figure 2 -

@@

# Figure 3

These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.

```{r}
cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = model, color = dist, y = BIC)) +
  geom_boxplot() +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Pooling Model", y = "Raw BIC values") +
  theme_classic() +
  guides(color=guide_legend(title = "Distribution model")) +
  theme(legend.position = "bottom")

@@

```{r fig.height=4}

@@

>>>>

# Figure 2 - Percent Support

@@

Figure 2 - Percent support for the different distribution models at the three pooling levels. Percent support is based on 1000 bootstrapped replicas for each scenario. Labels on the x axis show the best fitting model for the original datasets. A) percent support at the three pooling levels, with CP having over 50% support for the lognormal distribution, in agreement with the model fit to the complete dataset. PP and NP scenarios show 100% support for the multi-distribution model, which considers the best fitting model for each family group or individual, respectively. B) Percent support for each model in the family groups. C) Support for each model at the individual level.

```{r eval=FALSE}
# These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
  ggplot(., aes(x = model, color = dist, y = BIC)) +
  geom_boxplot() +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Pooling Model", y = "Raw BIC values") +
  theme_classic() +
  guides(color=guide_legend(title = "Distribution model")) +
  theme(legend.position = "bottom")

@@

```{r eval=FALSE, fig.height=4}

@@

```{r fig.height=4}
cp.bic %>% 
  bind_rows(., pp.bic) %>% 
  bind_rows(., np.bic) %>% 
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
  facet_wrap(~model, nrow = 3) +
  #geom_col() +
  geom_point(alpha = 0.8, shape = 15) +
  scale_color_manual(values = cols.fig2) +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Bootstrap replicates", x = "BIC units from best model") +
  theme(legend.position = "right") +
  guides(color=guide_legend(title = "Distribution \n model"))
```
